Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 introduction.tex
Fix bibliography

This state-of-practice paper provides three main contributions:  (i) a critical
evaluation of the many design and operational considerations that have been
taken to support the sustained, scalable and production usage of Titan for
historically high-throughput workloads; (ii) a preliminary characterization of a
next generation executor (NGE) for PanDA to support non-traditional
heterogeneous workloads and execution modes;  and (iii) early lessons and
guidance for how current and future experimental and observational systems can
be integrated with production supercomputers in a general and extensible manner.

% As the community looks forward to designing the next generation of online
% analytical platforms~\cite{foap-url}, this project provides some

>>>>

This state-of-practice paper provides three main contributions:  (i) a critical
evaluation of the many design and operational considerations that have been
taken to support the sustained, scalable and production usage of Titan for
historically high-throughput workloads; (ii) a preliminary characterization of a
next generation executor (NGE) for PanDA to support non-traditional
heterogeneous workloads and execution modes;  and (iii) early lessons and
guidance as the community looks forward to designing the next generation of
online analytical platforms~\cite{foap-url}, for how current and future
experimental and observational systems can be integrated with production
supercomputers in a general and extensible manner.
